% ----------------------------------------------------------------------------
% Nonfunctional Requirements
% ----------------------------------------------------------------------------
\chapter{Other Nonfunctional Requirements}

\section{Performance Requirements}
\iffalse
$<$If there are performance requirements for the product under various 
circumstances, state them here and explain their rationale, to help the 
developers understand the intent and make suitable design choices. Specify the 
timing relationships for real time systems. Make such requirements as specific 
as possible. You may need to state performance requirements for individual 
functional requirements or features.$>$
\fi

There are no performance requirements as of now.

\section{Safety Requirements}
\iffalse
$<$Specify those requirements that are concerned with possible loss, damage, or 
harm that could result from the use of the product. Define any safeguards or 
actions that must be taken, as well as actions that must be prevented. Refer to 
any external policies or regulations that state safety issues that affect the 
product’s design or use. Define any safety certifications that must be 
satisfied.$>$
\fi
All input data are treated as read only. They should not be deleted.

\section{Security Requirements}
\iffalse
$<$Specify any requirements regarding security or privacy issues surrounding use 
of the product or protection of the data used or created by the product. Define 
any user identity authentication requirements. Refer to any external policies or 
regulations containing security issues that affect the product. Define any 
security or privacy certifications that must be satisfied.$>$
\fi
All Digital Globe (WorldView) imagery is proprietary and cannot be released publically. 
Use of imagery must be in accordance with the guidelines and requirements of the Polar 
Geospatial Center and the NGA NextView License. 

\section{Software Quality Attributes}
\iffalse
$<$Specify any additional quality characteristics for the product that will be 
important to either the customers or the developers. Some to consider are: 
adaptability, availability, correctness, flexibility, interoperability, 
maintainability, portability, reliability, reusability, robustness, testability, 
and usability. Write these to be specific, quantitative, and verifiable when 
possible. At the least, clarify the relative preferences for various attributes, 
such as ease of use over ease of learning.$>$\fi

The software should be accompanied with detailed documentation, and examples that demonstrate its usage. In addition, the source code should publicly available through Github.

